---
title: "Introduction: Infant mortality in Sweden"
author: "Bayesian COP : Practical application 2"
date: "9/15/2021"
output: html_document
---

Treated in John Bryant 's book [Bayesian Demographic Estimation and Forecasting (2019)](https://ebookcentral.proquest.com/lib/statsnz/detail.action?docID=5437058)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. The data

The data is available as part of a package and is made of 2 files: infant deaths, and births

### 1.1 download the package

```{r, message = FALSE}
library(devtools)
install_github("johnrbryant/bdefdata")
```

### 1.2. load the data

```{r, message = FALSE}
library(bdefdata)
deaths <- bdefdata::sweden_deaths
births <- bdefdata::sweden_births
```


## 2. Aim

Our aim is to estimate Swedish infant mortality rate across regions and time (10-year time period). Modelling allows us to ask questions such as "Are regions struggling more than others to keep babies alive?" or "Is infant survival improving over time?".

## 3. Things to consider/ponder on

- The data captures all of the target population, by county and year.

- The definition of infant mortality rate merits some thought

- Prior choice will be critical here: look up structured priors!

- Any opportunity for a multilevel setup?


## 4. Potential help:

- Obviously [Bryant' s book](https://ebookcentral.proquest.com/lib/statsnz/detail.action?docID=5437058) and [its associated website](https://www.bdef-book.com/code), but try to address the poblem as if it was never treated before: YOU are the statistician and Bryant' s treatment of the problem wasn' t necessarily the only modelling option.

- [BDA](https://ebookcentral.proquest.com/lib/statsnz/detail.action?docID=1438153) chapters 3, 5, 14, 15

- Vic is a precious repository of knowledge on count models

- Steve can tell you about time series and orient you towards resources if you are interested to explore that way. [Hooten & Hefley](https://ebookcentral.proquest.com/lib/statsnz/detail.action?docID=5775185), chapter 16, also covers Bayesian time series

- THE TEAMS CHANNEL CHAT! Remember to turn on notifications.

